---
title: "Evaluations of positive and negative stimuli using the Affective Misattribution Procedure (AMP) and self-reports"
subtitle: "Analysis"
author: "Template: Ian Hussey; content: [Student name]"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

# set knit options
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

# disable scientific notation
options(scipen = 999) 

```

# Dependencies

```{r}

library(patchwork)
library(tidyverse)
library(knitr)
library(kableExtra)
library(janitor)
library(scales)
library(RColorBrewer)
library(ggplot2)
library(ggridges)
library(ggrain)
library(gridExtra)

```

# Data

Load the processed data and apply the global exclusions.

```{r}

data_processed <- read_csv("../data/processed/data_processed.csv")

data_processed_after_exclusions <- data_processed |>
  filter(exclude_participant == "include")

```

# Sample descriptives

## Sample size before exclusions

```{r}

data_processed |>
  count(name = "n") |>
  kable() |>
  add_header_above(header = c("Whole sample" = 1)) |> # note that you can add header rows to tables like this. The "1" indicates the number of columns the header should span. The sum of these numbers must equal the number of columns or you'll get an error.
  kable_classic(full_width = FALSE)

```

## Sample size after exclusions

Sample used in subsequent analyses

```{r}

data_processed_after_exclusions |>
  count(name = "n") |>
  kable() |>
  add_header_above(header = c("For analysis" = 1)) |>
  kable_classic(full_width = FALSE)

```

## Age

```{r}

data_processed_after_exclusions |>
  mutate(age = as.numeric(age)) |>
  summarise(Mean = mean(age, na.rm = TRUE),
            SD = sd(age, na.rm = TRUE)) |>
  mutate_all(.funs = janitor::round_half_up, digits = 1) |>
  kable() |>
  add_header_above(header = c("Age" = 2)) |>
  kable_classic(full_width = FALSE)

```

## Gender

```{r}

data_processed_after_exclusions |> 
  rename(Gender = gender) |>
  group_by(Gender) |> 
  summarise(n = n()) |> 
  mutate(Percent = paste0(round_half_up((n / sum(n)) * 100, 1), "%")) |>
  mutate(Gender = stringr::str_to_sentence(Gender)) |> # Change the case of the Gender variable so that it prints nicely
  kable() |>
  kable_classic(full_width = FALSE)

```

# Descriptives

Descriptive statistics and plots of the measures (excluding the demographics variables)

## Self-reported evaluations

### Descriptive stats

```{r}

# overall self-reported evaluations
dat_mean_ratings <- data_processed_after_exclusions |>
  summarise(Mean = mean(mean_evaluation, na.rm = TRUE),
            SD = sd(mean_evaluation, na.rm = TRUE),
            n = n()) |>
  mutate(group = "Full sample")

# self-reported evaluations by gender category
dat_mean_ratings_by_gender <- data_processed_after_exclusions |>
  group_by(group = gender) |>
  summarise(Mean = mean(mean_evaluation, na.rm = TRUE),
            SD = sd(mean_evaluation, na.rm = TRUE),
            n = n())

# combine both into one table
bind_rows(dat_mean_ratings,
          dat_mean_ratings_by_gender) |>
  select(Subset = group, Mean, SD, n) |> # select variables of interest, and rename one 
  mutate(Subset = stringr::str_to_sentence(Subset)) |> # Change the case of the Subset variable so that it prints nicely
  mutate_if(is.numeric, round_half_up, digits = 2) |>
  kable() |>
  add_header_above(header = c(" " = 1, "Self-reported evaluations" = 3)) |>
  kable_classic(full_width = FALSE)

```

### Descriptive plot

```{r}

ggplot(data_processed_after_exclusions, aes(x = mean_evaluation)) +
  geom_histogram(binwidth = 1,
                 boundary = 0,
                 fill = viridis_pal(begin = 0.45, option = "mako")(1), 
                 color = viridis_pal(begin = 0.30, option = "mako")(1)) + 
  xlab("Mean self-reported evaluation") +
  ylab("Frequency") +
  theme_linedraw() +
  scale_x_continuous(breaks = pretty_breaks(n = 7)) +
  coord_cartesian(xlim = c(1, 7)) +
  theme(panel.grid.minor = element_blank())

```

## AMP evaluations

### Descriptive stats

\TODO add table of means, SDs, Ns

```{r}


```

### Descriptive plots

```{r}

ggplot(data_processed_after_exclusions, aes(x = AMP_score)) +
  geom_histogram(binwidth = 0.05,
                 boundary = 0,
                 fill = viridis_pal(begin = 0.45, option = "mako")(1), 
                 color = viridis_pal(begin = 0.30, option = "mako")(1)) + 
  xlab("AMP score") +
  ylab("Frequency") +
  theme_linedraw() +
  scale_x_continuous(breaks = pretty_breaks(n = 10))

```

# Analyses & hypothesis tests

## Self-reported evaluations are correlated with evaluations on the AMP

### Plot

```{r}

ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  geom_smooth(method = "lm",
              color = viridis_pal(begin = 0.45, option = "mako")(1)) +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_linedraw() 

ggplot(data_processed_after_exclusions, 
       aes(y = AMP_score,
           x = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  geom_smooth(method = "lm",
              color = viridis_pal(begin = 0.45, option = "mako")(1)) +
  ylab("AMP score") +
  xlab("Mean self-reported evaluation") +
  theme_linedraw() 

ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_linedraw() 

```

More complex plots:

#### Axial hisograms

Scatter plots with axial histograms using ggExtra: https://cran.r-project.org/web/packages/ggExtra/vignettes/ggExtra.html

\TODO add axial histograms to a scatter plot. In a single plot, present different regression lines split by gender, and separate axial histograms for each gender.

```{r}
axialhisto<-ggplot(data_processed_after_exclusions, 
                   aes(x = AMP_score,
                       y = mean_evaluation, colour= gender))+
  geom_point() +
  scale_colour_discrete(name = "gender",
                        labels = c("male", "female", "non_binary"))


ggMarginal(axialhisto, type = "histogram", groupColour=TRUE, groupFill=TRUE)
ggMarginal(axialhisto, type = "density", groupColour=TRUE, groupFill=TRUE)

```

#### Labelled points

Label points using ggrepel: https://cran.r-project.org/web/packages/ggrepel/vignettes/ggrepel.html

\TODO Label the points in a scatter plot using their participant codes. Label only the participants with more extreme scores.

```{r}

 labelledplot<-ggplot(data_processed_after_exclusions, 
            aes(x = AMP_score,
                y = mean_evaluation, label= subject))+
    geom_point(color = "red")

labelledplotfinal <- labelledplot + geom_text_repel() + labs(title = "geom_text_repel()")
labelledplotfinal


colors <- viridis_pal(begin = 0.0, end = 1.0, option = "mako")(10)

colors

show_col(colors)

```

#### Magnify areas

Magnify areas of your plot with ggmagnify: https://hughjonesd.github.io/ggmagnify/

\TODO Magnify an area of one of your scatter plots, eg where there are a lot of data points in a small area.

```{r}

ggmagnifyplot <- ggplot(data_processed_after_exclusions, aes(x = AMP_score, y = mean_evaluation, label= subject)) +
    geom_point(color = "red")

from <- c(xmin = 0.45, xmax = 0.68, ymin = 0.85, ymax = 1.1)
to <- c(xmin = 0.00, xmax = 0.4, ymin = 4, ymax = 5.5)

ggmagnifyplotfinal<-ggmagnifyplot + geom_magnify(aes(x = AMP_score, y = mean_evaluation), from = from, to = to)

ggmagnifyplotfinal

```

### Test

\TODO run an appropriate test. Below the output, interpret the results. Consider using `easystats::report()`, but you can do this manually if you prefer.

```{r}
# From the plots it looks like only AMP evaluations are approx. normally distributed, whereas self reported evaluations are not
# Therefore, instead of a pearson test,I use the spearman test to investigate the correlation between these two variables

cor.test(data_processed_after_exclusions$mean_evaluation, data_processed_after_exclusions$AMP_score, method = "spearman", exact=FALSE)

# The p-value (0.2) is rather large, so we cannot reject the hypotheses that the two variables are not correlated
# The results suggest that both variables are not correlated

```

## Self-reported evalautions differ between men and women

### Plot

\TODO split histogram, split violin plot, raincloud plot, etc.

```{r}
facet_order <- c( "female", "male","nonbinary")
legend_labels <- c( "Female", "Male","Non-Binary")

dark2_colors <- brewer.pal(3, "Dark2")
print(dark2_colors)

plot <- ggplot(data_processed_after_exclusions, 
               aes(x = gender,
                   y = mean_evaluation, colour = gender)) +
  geom_point() +
  scale_colour_manual(values = dark2_colors) +  # Verwende die Dark2-Farben
  labs(title = "Scatter Plot of mean evaluation by Gender", x = "Gender", y = "Mean Evaluation")

plot

# split histogram plot
histogramplot_SR <- ggplot(data_processed_after_exclusions, aes(x = mean_evaluation, fill = gender)) +
  geom_histogram(binwidth = 0.2, color = "white", alpha = 0.7) +
  coord_cartesian(xlim = c(min(data_processed_after_exclusions$mean_evaluation), max(data_processed_after_exclusions$mean_evaluation)))  +
  labs(title = "Histogram of self-reported evaluation by Gender", x = "self-reported evaluation", y = "Frequency") +
  scale_fill_manual(values = dark2_colors, name = "Gender", breaks = facet_order, labels=legend_labels)
histogramplot_SR

histogramplot_SR_better <- ggplot(data_processed_after_exclusions, aes(x = mean_evaluation, fill = gender)) +
  geom_histogram(binwidth = 0.2, color = "white", alpha = 0.7) +
  coord_cartesian(xlim = c(min(data_processed_after_exclusions$mean_evaluation), max(data_processed_after_exclusions$mean_evaluation))) +
  facet_wrap(~ gender, scales = "free") +
  labs(title = "Histogram of self-reported mean evaluation by Gender", x = "self-reported mean evaluation", y = "Frequency") +
  scale_fill_manual(values = dark2_colors)+
  guides(fill = FALSE) 
histogramplot_SR_better

#rviolin plot
violinplot_SR<-ggplot(data_processed_after_exclusions, aes(x = gender, y = mean_evaluation, fill = gender)) +
  geom_violin() +
  scale_fill_manual(values = dark2_colors, name = "Gender", breaks = facet_order, labels=legend_labels)+
  scale_x_discrete(name = "gender",
                   labels = legend_labels) +
  theme_classic() +
  labs(title = "Histogram of self-reported mean evaluation by Gender", x = "self-reported evaluation", y = "Self-report Mean") +
  guides(fill = FALSE)

violinplot_SR
#raincloud plot

raincloudplot_SR_overlapped <- ggplot(data_processed_after_exclusions, 
                         aes(x = 1, y = mean_evaluation, fill = gender)) +
  geom_rain(alpha = 0.5) +
  scale_fill_manual(values = dark2_colors, name = "Gender", breaks = facet_order, labels=legend_labels)+
  scale_x_discrete(name = "gender",
                   labels = legend_labels)+
  labs(title = "Raincloud Plot of self-report mean evaluation by Gender", x = "Gender", y = "Mean Evaluation")

raincloudplot_SR_overlapped

raincloudplot_SR <- ggplot(data_processed_after_exclusions, 
                         aes(x = gender, y = mean_evaluation, fill = gender)) +
  geom_rain(alpha = 0.5) +
  scale_fill_manual(values = dark2_colors) +
  labs(title = "Raincloud Plot of self-report mean evaluation by Gender", x = "Gender", y = "Mean Evaluation")+
  guides(fill = FALSE) 

raincloudplot_SR

```

### Test

\TODO run an appropriate test. Below the output, interpret the results: write a few sentences that report and interpret the results following APA reporting style.

```{r}

# Assumption from plots: self reported evaluations are NOT normally distributed

# Using the Wilcoxon Rank-Sum to see if evaluations are different between men and woman

# Wilcoxon rank-sum test
wilcox_test_result <- wilcox.test(mean_evaluation ~ gender, data = subset(data_processed_after_exclusions, gender!='nonbinary'), exact=FALSE)

print(wilcox_test_result)

# Results suggest that there is a difference in self reported evaluations between male and female


```

## Evaluations on the Affect Misattribution Procedure differ between men and women

### Plot

\TODO split histogram, split violin plot, raincloud plot, etc.

This time, vary the labeling and order of the legend, e.g., capitalise "Men" and "Women", and know how to change the order of the factors.

```{r}

#Split histogram
histogramplot_AMP <- ggplot(data_processed_after_exclusions, aes(x = AMP_score, fill = factor(gender))) +
  geom_histogram(binwidth = 0.05, color = "white", alpha = 0.7) +
  coord_cartesian(xlim = c(min(data_processed_after_exclusions$AMP_score), max(data_processed_after_exclusions$AMP_score))) +
  facet_wrap(~ gender, scales = "free") +
  labs(title = "Histogram of AMP_score by Gender", x = "AMP_score", y = "Frequency") +
  scale_fill_manual(values = dark2_colors, name = "Gender", breaks = c("nonbinary", "female", "male"))
histogramplot_AMP

facet_order <- c( "female", "male","nonbinary")
legend_labels <- c( "Female", "Male","Non-Binary")

histogramplot_AMP_2 <- ggplot(data_processed_after_exclusions, 
                                  aes(x = AMP_score, fill = factor(gender))) +
  geom_histogram(binwidth = 0.05, color = "white", alpha = 0.7) +
  coord_cartesian(xlim = c(min(data_processed_after_exclusions$AMP_score), max(data_processed_after_exclusions$AMP_score))) +
  facet_wrap(~ factor(gender, levels = facet_order), scales = "free") +
  labs(title = "Histogram of AMP_score by Gender", x = "AMP_score", y = "Frequency") +
  scale_fill_manual(values = dark2_colors, name = "Gender", breaks = facet_order, labels=legend_labels)
histogramplot_AMP_2

#Split violin plot

violin_AMP<-ggplot(data_processed_after_exclusions, aes(x = gender, y = AMP_score, fill = gender)) +
  geom_violin() +
   scale_fill_manual(values = dark2_colors, name = "Gender", breaks = facet_order, labels=legend_labels)+
  scale_x_discrete(name = "gender",
                   labels = legend_labels)  +
  theme_classic()  +
  scale_y_continuous(name = "AMP_score")
violin_AMP

#Split raincloud plot
raincloudplot_AMP <- ggplot(data_processed_after_exclusions, 
                         aes(x = gender, y = AMP_score, fill = gender)) +
  geom_rain(alpha = 0.5) +
  scale_fill_manual(values = dark2_colors) +
  labs(title = "Raincloud Plot of AMP_score by Gender", x = "Gender", y = "AMP_score") +
  scale_fill_manual(values = dark2_colors, name = "Gender", breaks = facet_order, labels=legend_labels)+scale_x_discrete(name = "gender",
                   labels = legend_labels) 
  
raincloudplot_AMP


```

### Test

\TODO run an appropriate test. Below the output, print an interpretation of the results generated by the 'easystats' package [report](https://easystats.github.io/report/). I.e., use `report::report()`.

```{r}

# Assumption from plots: AMP Score is approx. normally distributed, plus we have a sample size > 30, so that the t-test can be performed

# Using the t-test to see if AMP_score are different between men and woman
# Shapiro-Wilk Test for normal distribution (male)
print(shapiro.test(subset(data_processed_after_exclusions, gender=='male')$mean_evaluation))
# Shapiro-Wilk Test for normal distribution (female)
print(shapiro.test(subset(data_processed_after_exclusions, gender=='female')$mean_evaluation))

# Both tests confirm the non-normal distribution
# Perform a t-test
t_test_result <- t.test(AMP_score ~ gender, data = subset(data_processed_after_exclusions, gender!='nonbinary'))

# Print the t-test result
print(t_test_result)

# Results suggest there is no significant difference in AMP evaluations between male and female


```

## Combining plots

Combine plots using the library [patchwork](https://patchwork.data-imaginist.com/).

\TODO Combine at least three of the above plots into one.

```{r}


histogramplot_AMP_2/violin_AMP/raincloudplot_AMP
#or
combineplot<-grid.arrange(histogramplot_AMP_2,violin_AMP,raincloudplot_AMP, ncol = 1)
```

## Saving plots

Save plots to disk with `ggsave()`

\TODO Save the above combined plot to disk as both .png and .pdf. Ensure the png has at least 300dpi resolution.

```{r}
dir.create("../plot/")

ggsave("../plot/combineplot.png",dpi = 300,combineplot)
ggsave("../plot/combineplot.pdf",dpi = 300,combineplot)

#or as the other plots

ggsave("../code/analysis_files/figure-html/combineplot.png",dpi = 300,combineplot)
ggsave("../code/analysis_files/figure-html/combineplot.pdf",dpi = 300,combineplot)

```

# Session info

```{r}

sessionInfo()

```



