---
title: "Evaluations of positive and negative stimuli using the Affective Misattribution Procedure (AMP) and self-reports"
subtitle: "Analysis"
author: "Template: Ian Hussey; content: [Annika Langner]"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

# set knit options
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

# disable scientific notation
options(scipen = 999) 

```

# Dependencies

```{r}



library(patchwork)
library(tidyverse)
library(knitr)
library(kableExtra)
library(janitor)
library(scales)
library(RColorBrewer)
library(ggplot2)
library(ggridges)
library(ggrain)
library(gridExtra)
library(psych)
library(ggExtra)
library(ggrepel)  
library(ggdist)
library(report)
library(ggmagnify)
library(crayon)

```

# Data

Load the processed data and apply the global exclusions.

```{r}

data_processed <- read_csv("../data/processed/data_processed.csv")

data_processed_after_exclusions <- data_processed |>
  filter(exclude_participant == "include")

```

# Sample descriptives

## Sample size before exclusions

```{r}
data_processed
data_processed |>
  count(name = "n") |>
  kable() |>
  add_header_above(header = c("Whole sample" = 1)) |> # note that you can add header rows to tables like this. The "1" indicates the number of columns the header should span. The sum of these numbers must equal the number of columns or you'll get an error.
  kable_classic(full_width = FALSE)

```

## Sample size after exclusions

Sample used in subsequent analyses

```{r}

data_processed_after_exclusions |>
  count(name = "n") |>
  kable() |>
  add_header_above(header = c("For analysis" = 1)) |>
  kable_classic(full_width = FALSE)

```

## Age

```{r}

data_processed_after_exclusions |>
  mutate(age = as.numeric(age)) |>
  summarise(Mean = mean(age, na.rm = TRUE),
            SD = sd(age, na.rm = TRUE)) |>
  mutate_all(.funs = janitor::round_half_up, digits = 1) |>
  kable() |>
  add_header_above(header = c("Age" = 2)) |>
  kable_classic(full_width = FALSE)

```

## Gender

```{r}

data_processed_after_exclusions |> 
  rename(Gender = gender) |>
  group_by(Gender) |> 
  summarise(n = n()) |> 
  mutate(Percent = paste0(round_half_up((n / sum(n)) * 100, 1), "%")) |>
  mutate(Gender = stringr::str_to_sentence(Gender)) |> # Change the case of the Gender variable so that it prints nicely
  kable() |>
  kable_classic(full_width = FALSE)

```

# Descriptives

Descriptive statistics and plots of the measures (excluding the demographics variables)

## Self-reported evaluations

### Descriptive stats

```{r}

# overall self-reported evaluations
dat_mean_ratings <- data_processed_after_exclusions |>
  summarise(Mean = mean(mean_evaluation, na.rm = TRUE),
            SD = sd(mean_evaluation, na.rm = TRUE),
            n = n()) |>
  mutate(group = "Full sample")

# self-reported evaluations by gender category
dat_mean_ratings_by_gender <- data_processed_after_exclusions |>
  group_by(group = gender) |>
  summarise(Mean = mean(mean_evaluation, na.rm = TRUE),
            SD = sd(mean_evaluation, na.rm = TRUE),
            n = n())

# combine both into one table
bind_rows(dat_mean_ratings,
          dat_mean_ratings_by_gender) |>
  select(Subset = group, Mean, SD, n) |> # select variables of interest, and rename one 
  mutate(Subset = stringr::str_to_sentence(Subset)) |> # Change the case of the Subset variable so that it prints nicely
  mutate_if(is.numeric, round_half_up, digits = 2) |>
  kable() |>
  add_header_above(header = c(" " = 1, "Self-reported evaluations" = 3)) |>
  kable_classic(full_width = FALSE)

```

### Descriptive plot

```{r}

ggplot(data_processed_after_exclusions, aes(x = mean_evaluation)) +
  geom_histogram(binwidth = 1,
                 boundary = 0,
                 fill = viridis_pal(begin = 0.45, option = "mako")(1), 
                 color = viridis_pal(begin = 0.30, option = "mako")(1)) + 
  xlab("Mean self-reported evaluation") +
  ylab("Frequency") +
  theme_linedraw() +
  scale_x_continuous(breaks = pretty_breaks(n = 7)) +
  coord_cartesian(xlim = c(1, 7)) +
  theme(panel.grid.minor = element_blank())

```

## AMP evaluations

### Descriptive stats

\TODO add table of means, SDs, Ns

```{r}


```

### Descriptive plots

```{r}

ggplot(data_processed_after_exclusions, aes(x = AMP_score)) +
  geom_histogram(binwidth = 0.05,
                 boundary = 0,
                 fill = viridis_pal(begin = 0.45, option = "mako")(1), 
                 color = viridis_pal(begin = 0.30, option = "mako")(1)) + 
  xlab("AMP score") +
  ylab("Frequency") +
  theme_linedraw() +
  scale_x_continuous(breaks = pretty_breaks(n = 10))

```

# Analyses & hypothesis tests

## Self-reported evaluations are correlated with evaluations on the AMP

### Plot

```{r}

ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  geom_smooth(method = "lm",
              color = viridis_pal(begin = 0.45, option = "mako")(1)) +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_linedraw() 

ggplot(data_processed_after_exclusions, 
       aes(y = AMP_score,
           x = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  geom_smooth(method = "lm",
              color = viridis_pal(begin = 0.45, option = "mako")(1)) +
  ylab("AMP score") +
  xlab("Mean self-reported evaluation") +
  theme_linedraw() 

ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_linedraw() 

```

More complex plots:

#### Axial hisograms

Scatter plots with axial histograms using ggExtra: https://cran.r-project.org/web/packages/ggExtra/vignettes/ggExtra.html

\TODO add axial histograms to a scatter plot. In a single plot, present different regression lines split by gender, and separate axial histograms for each gender.

```{r}
facet_order <- c( "female", "male","nonbinary")
legend_labels <- c( "Female", "Male","Non-Binary")

dark2_colors <- brewer.pal(3, "Dark2")

axialhisto <- ggplot(data_processed_after_exclusions, 
                     aes(x = AMP_score,
                         y = mean_evaluation, colour = gender)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  scale_colour_manual(name = "Gender", values = dark2_colors, breaks = facet_order, labels=legend_labels)+
  labs(title = "Distribution and relationship: Self report and AMP",x = "AMP score", y = "Mean self-reported evaluation")+
  theme_linedraw() 

scatterPlot_axialhisto<-ggMarginal(axialhisto, type = "histogram", groupColour=TRUE, groupFill=TRUE)
scatterPlot_axialhisto

#scatterPlot_axialdensity<-ggMarginal(axialhisto, type = "density", groupColour=TRUE, groupFill=TRUE)
#scatterPlot_axialdensity
```

#### Labelled points

Label points using ggrepel: https://cran.r-project.org/web/packages/ggrepel/vignettes/ggrepel.html

\TODO Label the points in a scatter plot using their participant codes. Label only the participants with more extreme scores.

```{r}

labelledplot<-ggplot(data_processed_after_exclusions, 
                     aes(x = AMP_score,
                         y = mean_evaluation, label= subject))+
  geom_point(color = "#D95F02")+
  labs(title = "Relationship: Self report and AMP",x = "AMP score", y = "Mean self-reported evaluation")+
  theme_linedraw() 

labelledplotfinal <- labelledplot + geom_text_repel() + labs(title = "Relationship: Self report and AMP with labeled points")
labelledplotfinal

cat("Informsation from the cours about colors")
colors <- viridis_pal(begin = 0.0, end = 1.0, option = "mako")(10)
show_col(colors)

```

#### Magnify areas

Magnify areas of your plot with ggmagnify: https://hughjonesd.github.io/ggmagnify/

\TODO Magnify an area of one of your scatter plots, eg where there are a lot of data points in a small area.

```{r}

cat("I used geom_jitter to better show the effect of magnify areas (instead of geom_point)")

from <- c(xmin = 0.50, xmax = 0.53, ymin = 0.85, ymax = 1.1)
to <- c(xmin = 0.0, xmax = 0.195, ymin = 3.5, ymax = 5.125)

scatterplot_magnify <- ggplot(data_processed_after_exclusions, aes(x = AMP_score, y = mean_evaluation)) +
    geom_jitter(color = "#D95F02")+
  labs(title = "Relationship: Self report and AMP with magnify areas",x = "AMP score", y = "Mean self-reported evaluation")+
  theme_linedraw() 

ggmagnifyplot<-scatterplot_magnify+ geom_magnify(from = from, to = to)+theme_linedraw()
ggmagnifyplot

```

### Test

\TODO run an appropriate test. Below the output, interpret the results. Consider using `easystats::report()`, but you can do this manually if you prefer.

```{r}
cortest<-cor.test(data_processed_after_exclusions$mean_evaluation, data_processed_after_exclusions$AMP_score, method = "spearman", exact=FALSE)

cat("From the plots it looks like only AMP scores are approx. normally distributed, whereas self-reported evaluations are not.\n  Therefore, instead of a pearson test,I used the spearman test to investigate the correlation between these two variables.\n  The p-value (0.2) is rather large, so we cannot reject the hypotheses that the two variables are not correlated.\n  The results suggest that both variables are not correlated.")

report(cortest)

```

## Self-reported evalautions differ between men and women

### Plot

\TODO split histogram, split violin plot, raincloud plot, etc.

```{r}
facet_order <- c( "male", "female","nonbinary")
legend_labels <- c( "Female", "Female","Non-Binary")
dark2_colors <- brewer.pal(3, "Dark2")

# split histogram plot
ggplot(data_processed_after_exclusions, aes(x = mean_evaluation, fill = gender)) +
  geom_histogram(binwidth = 0.2, color = "white", alpha = 0.8) +
  facet_wrap(~ gender, scales = "free") +
  labs(title = "Histogram of Mean self-reported evaluation by Gender with Free Scales", x = "Mean self-reported evaluation", y = "Frequency") +
  scale_fill_manual(values = dark2_colors) +
  guides(fill = "none") + 
  theme_bw()

ggplot(data_processed_after_exclusions, aes(x = mean_evaluation, fill = gender)) +
  geom_histogram(binwidth = 0.2, color = "white", alpha = 0.8) +
  facet_wrap(~ gender, scales = "fixed") +
  labs(title = "Histogram of Mean self-reported evaluation by Gender with Fixed Scales", x = "Mean self-reported evaluation", y = "Frequency") +
  scale_fill_manual(values = dark2_colors) +
  guides(fill = "none") + 
  theme_bw() +
  scale_y_continuous(breaks = seq(0, 30, by = 5))

cat("Adjusting the y-axis and background grid")
ggplot(data_processed_after_exclusions, aes(x = mean_evaluation, fill = gender)) +
  geom_histogram(binwidth = 0.2, color = "white", alpha = 0.8) +
  facet_wrap(~ gender, scales = "fixed") +
  labs(title = "Histogram of Mean self-reported evaluation by Gender with Fixed Scales", x = "Mean self-reported evaluation", y = "Frequency") +
  scale_fill_manual(values = dark2_colors) +
  guides(fill = "none") + 
  theme_bw() +
  scale_y_continuous(breaks = seq(0, 32, by = 4))+
  geom_hline(yintercept = seq(0, 32, by = 2), color = "gray",  alpha = 0.5)

#violin plot
ggplot(data_processed_after_exclusions, aes(x = gender, y = mean_evaluation, fill = gender)) +
  geom_violin() +
  scale_fill_manual(values = dark2_colors, name = "Gender", breaks = facet_order, labels=legend_labels)+
  labs(title = "Violin plot of Mean self-reported evaluation by Gender", x = "Gender", y = "Mean self-reported evaluation") +
  guides(fill = "none") + 
  theme_bw() 

#raincloud plot
ggplot(data_processed_after_exclusions, aes(x = gender, y = mean_evaluation, fill = gender)) + 
 stat_halfeye(adjust = 0.5,justification = -0.2, .width = 0,point_colour = NA) + 
  scale_fill_manual(values = dark2_colors) +
  labs(title = "Raincloud plot of Mean self-reported evaluation by Gender", x = "Gender", y = "Mean self-reported evaluation")+
  geom_boxplot(width = .1, outlier.shape = NA) +
  ggdist::stat_dots(side = "left", dotsize = .4, justification = 1.1,color="black", binwidth = .1)+
  theme_bw() +
  guides(fill = "none") + 
  coord_flip()

ggplot(data_processed_after_exclusions, aes(x = gender, y = mean_evaluation, fill = gender)) +
  geom_rain(alpha = 0.8) +
  scale_fill_manual(values = dark2_colors) +
  labs(title = "Raincloud plot of Mean self-reported evaluation by Gender", x = "Gender", y = "Mean self-reported evaluation")+
  guides(fill = "none") + 
  coord_flip()+
  theme_bw() 

```

### Test

\TODO run an appropriate test. Below the output, interpret the results: write a few sentences that report and interpret the results following APA reporting style.

```{r}

cat("Assumption from plots: self reported evaluations are NOT normally distributed. Also the shapiro tests support this. Therefore, I used the Wilcoxon rank-sum test.") 
print(shapiro.test(subset(data_processed_after_exclusions, gender=='male')$mean_evaluation))
print(shapiro.test(subset(data_processed_after_exclusions, gender=='male')$mean_evaluation))

# Wilcoxon rank-sum test
wilcox_test_result <- wilcox.test(mean_evaluation ~ gender, data = subset(data_processed_after_exclusions, gender!="nonbinary"), exact=FALSE)
wilcox_test_result

cat(" Wilcoxon rank-sum test was conducted to compare self-reported mean evaluation scores between male and female participants. The results revealed a statistically significant difference between males and females, ",italic("W")," = 622.5, ",italic("p"),"< 0.01. The median self-reported evaluation score was higher for males (",italic("M"),"=1.81) than for females (",italic("M"),"=1.32).")

mean_female <- data_processed_after_exclusions|>
  filter(gender == "female")|>
  summarize(mean_evaluation = mean(mean_evaluation)) 

mean_male <- data_processed_after_exclusions|>
  filter(gender == "male")|>
  summarize(mean_evaluation = mean(mean_evaluation)) 

# t-test, n>30: therefore, one could also use the t-test.
t_test_result_sr <- t.test(mean_evaluation ~ gender, data = subset(data_processed_after_exclusions, gender!="nonbinary"))
report(t_test_result_sr)

cat(" T-test was conducted to compare self-reported mean evaluation scores between male and female participants. The results revealed a statistically significant difference between males and females, ",italic("t")," (83.14)= -2.62, ",italic("p"),"< 0.01. The median self-reported evaluation score was higher for males (",italic("M"),"=1.81) than for females (",italic("M"),"=1.32).")

```
additional task: Alpha

```{r}
#additional task: calculate the alphabet
alpha(subset(data_processed_after_exclusions, select = c(prefer, like, positive)), check.keys =TRUE)
c("additional task: alpha=0.876904")
```


## Evaluations on the Affect Misattribution Procedure differ between men and women

### Plot

\TODO split histogram, split violin plot, raincloud plot, etc.

This time, vary the labeling and order of the legend, e.g., capitalise "Men" and "Women", and know how to change the order of the factors.

```{r}
#First order and labeling (first version)
facet_order_1 <- c( "female", "male","nonbinary")
facet_labels_1 <- c( "Female", "Male","Non-Binary")

#Second order and labeling (second version)
facet_order_2 <- c( "male", "female","nonbinary")
facet_labels_2 <- c( "male", "female","non-binary")

#Histogram with the first version of facet_order and facet_labels
cat("Histogram with the first version of facet_order and facet_labels")

ggplot(data_processed_after_exclusions, aes(x = AMP_score, fill = factor(gender))) +
  geom_histogram(binwidth = 0.05, color = "white", alpha = 0.8) +
  coord_cartesian(xlim = c(min(data_processed_after_exclusions$AMP_score), max(data_processed_after_exclusions$AMP_score))) +
  facet_wrap(~ factor(gender, levels = facet_order), scales = "fixed") +
  labs(title = "Histogram of AMP score by Gender: Version 1", x = "AMP score", y = "Frequency") +
  scale_fill_manual(values = dark2_colors, name = "Gender", breaks = facet_order_1, labels=facet_labels_1)+
  theme_bw() 

#Histogram with the second version of facet_order and facet_labels
cat("Histogram with the second version of facet_order and facet_labels")

ggplot(data_processed_after_exclusions, aes(x = AMP_score, fill = factor(gender))) +
  geom_histogram(binwidth = 0.05, color = "white", alpha = 0.8) +
  coord_cartesian(xlim = c(min(data_processed_after_exclusions$AMP_score), max(data_processed_after_exclusions$AMP_score))) +
  facet_wrap(~ factor(gender, levels = facet_order), scales = "fixed") +
  labs(title = "Histogram of AMP score by Gender: Version 2", x = "AMP score", y = "Frequency") +
  scale_fill_manual(values = dark2_colors, name = "Gender", breaks = facet_order_2, labels=facet_labels_2)+
  theme_bw()

#Violin plot with the first version of facet_order and facet_labels
cat("Violin plot with the first version of facet_order and facet_labels.")

violin_AMP_1<-ggplot(data_processed_after_exclusions, aes(x = gender, y = AMP_score, fill = gender)) +
  geom_violin(alpha = 0.8) +
  scale_fill_manual(values = dark2_colors, name = "Gender", breaks = facet_order_1, labels=facet_labels_1)+
  theme_bw()  +
  labs(title = "Violin plot of AMP score by Gender: Version 1", x = "Gender", y = "AMP score") 
violin_AMP_1

#Violin plot with the second version of facet_order and facet_labels
cat("Violin plot with the second version of facet_order and facet_labels.")

violin_AMP_2<-ggplot(data_processed_after_exclusions, aes(x = gender, y = AMP_score, fill = gender)) +
  geom_violin(alpha = 0.8) +
  scale_fill_manual(values = dark2_colors, name = "Gender", breaks = facet_order_2, labels=facet_labels_2)+
  theme_bw()  +
  labs(title = "Violin plot of AMP score by Gender: Version 2", x = "Gender", y = "AMP score") 
violin_AMP_2

#Split raincloud plot
ggplot(data_processed_after_exclusions, aes(x = gender, y = AMP_score, fill = gender)) +
  geom_rain(alpha = 0.8) +
  scale_fill_manual(values = dark2_colors) +
  labs(title = "Raincloud Plot of AMP score by Gender", x = "Gender", y = "AMP score") +
  scale_fill_manual(values = dark2_colors, name = "Gender", breaks = facet_order_2, labels=facet_labels_2)+
  scale_x_discrete(name = "Gender",labels = facet_labels_2) +
  theme_bw()

ggplot(data_processed_after_exclusions, aes(x = gender, y = AMP_score, fill = gender)) +
  geom_rain(alpha = 0.8) +
  scale_fill_manual(values = dark2_colors) +
  labs(title = "Raincloud Plot of AMP score by Gender", x = "Gender", y = "AMP score") +
  scale_fill_manual(values = dark2_colors, name = "Gender", breaks = facet_order_1, labels=facet_labels_1)+
  scale_x_discrete(name = "Gender",labels = facet_labels_1) +
  coord_flip()+
  theme_bw()

#For the combined plot: Single plots without legend and without title
data_processed_after_exclusions$gender <- factor(data_processed_after_exclusions$gender, levels = facet_order_1)
facet_labels_custom <- c("female" = "Female", "male" = "Male ", "nonbinary"="Non-Binary")

histogramplot_AMP <- ggplot(data_processed_after_exclusions, aes(x = AMP_score, fill = gender)) +
  geom_histogram(binwidth = 0.05, color = "white", alpha = 0.8) +
  coord_cartesian(xlim = c(min(data_processed_after_exclusions$AMP_score), max(data_processed_after_exclusions$AMP_score)))+
  scale_x_continuous(breaks = c(0, 0.5, 1)) +
  labs(x = "AMP score", y = "Frequency") +
  facet_wrap(~ gender, scales = "fixed", labeller = as_labeller(facet_labels_custom))+
  scale_fill_manual(values = dark2_colors, name = "Gender", breaks = facet_order_1, labels = facet_order_1) +
  theme_bw() +
  guides(fill = FALSE)

# Violin plot
violin_AMP <- ggplot(data_processed_after_exclusions, aes(x = gender, y = AMP_score, fill = gender)) +
  geom_violin(alpha = 0.8) +
  scale_fill_manual(values = dark2_colors) +
  theme_bw() +
  guides(fill = "none") + 
  scale_x_discrete(name = "", labels = facet_labels_1)+
  labs(x = "", y = "AMP score")

# Raincloud plots 
raincloudplot_AMP_h<-ggplot(data_processed_after_exclusions, aes(x = gender, y = AMP_score, fill = gender)) +
  geom_rain(alpha = 0.8) +
  scale_fill_manual(values = dark2_colors) +
  labs( x = "Gender", y = "AMP score") +
  scale_x_discrete(name = "gender",labels = facet_labels_1) +
  scale_x_discrete(name = "", labels = facet_labels_1)+
  theme_bw()+
  guides(fill = "none") 

raincloudplot_AMP_v <- ggplot(data_processed_after_exclusions, aes(x = gender, y = AMP_score, fill = gender)) +
  geom_rain(alpha = 0.8) +
  labs( x = "Gender", y = "AMP score") +
  scale_fill_manual(values = dark2_colors)+
  coord_flip()+
  guides(fill = "none") + 
  scale_x_discrete(name = "", labels = facet_labels_1)+
  theme_bw()

```

### Test

\TODO run an appropriate test. Below the output, print an interpretation of the results generated by the 'easystats' package [report](https://easystats.github.io/report/). I.e., use `report::report()`.

```{r}

# Assumption from plots: AMP Score is approx. normally distributed, plus we have a sample size > 30, so that the t-test can be performed

# Using the t-test to see if AMP_score are different between men and woman

# t-test
t_test_result_amp <- t.test(AMP_score ~ gender, data = subset(data_processed_after_exclusions, gender!="nonbinary"))

report(t_test_result_amp)
# Results suggest there is no significant difference in AMP scores between male and female

# Shapiro-Wilk Test for normal distribution (male)
print(shapiro.test(subset(data_processed_after_exclusions, gender=='male')$AMP_score))
# Shapiro-Wilk Test for normal distribution (female)
print(shapiro.test(subset(data_processed_after_exclusions, gender=='female')$AMP_score))
# Both tests confirm the non-normal distribution

# Wilcoxon rank-sum test
wilcox_test_result <- wilcox.test(AMP_score ~ gender, data = subset(data_processed_after_exclusions, gender!='nonbinary'), exact=FALSE)
wilcox_test_result
cat("The Wilcoxon test also confirm the results from the t-test. However, one can also use the t-test as n>30.")

```

## Combining plots

Combine plots using the library [patchwork](https://patchwork.data-imaginist.com/).

\TODO Combine at least three of the above plots into one.

```{r}

combineplot_h<-histogramplot_AMP/violin_AMP/raincloudplot_AMP_h
combineplot_v<-((histogramplot_AMP/ violin_AMP)|raincloudplot_AMP_v)+plot_annotation(title = 'Distribution of AMP score by gender')
#or
#combineplot<-grid.arrange(histogramplot_AMP_1,violin_AMP_1,raincloudplot_AMP, ncol = 1)
combineplot_v
combineplot_h

```

## Saving plots

Save plots to disk with `ggsave()`

\TODO Save the above combined plot to disk as both .png and .pdf. Ensure the png has at least 300dpi resolution.

```{r}
dir.create("../plot/")

ggsave("../plot/combineplot.png",dpi = 300,combineplot_v)
ggsave("../plot/combineplot.pdf",dpi = 300,combineplot_v)

```

# Session info

```{r}

sessionInfo()

```



